On Secure Delegation of SampBQP with a Classical Client

### 2020-01-19 preliminaries.tex
Move QFHE basics into preliminaries

>>>>

\subsection{Quantum Homomorphic Encryption Schemes}

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.

As this is a homomorphic encryption scheme, it satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$

We also recall the security definition for a FHE scheme.

\begin{dfn}
	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
	\Ethan{Urmila didn't specify quantum adversary here? Also dropped the $1^L$.}
\end{dfn}

Lastly, we recall the definition of a verifiable quantum FHE scheme:
\begin{dfn}
	TODO
\end{dfn}

### 2020-01-19 privacy.tex
Move QFHE basics into preliminaries

We present the interface of quantum full homomorphic encryption (QFHE) scheme as given in \cite{mahadev_qfhe}.

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.
As this is a homomorphic encryption scheme, it satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$

$\mathsf{Keygen}$ and $\mathsf{Enc}$ can be done classically. $\mathsf{Dec}$ commutes with standard basis measurement, and in the event that the result is already a measurement result, can also be done classically.

We also recall the security definition for a FHE scheme.

\begin{dfn}
	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
	$$\abs{Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, evk, \mathsf{HE.Enc}_{pk}(1))=1]}=\mu(\lambda)$$
	where $(pk, evk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
	\Ethan{Urmila didn't specify quantum adversary here? Also dropped the $1^L$.}
\end{dfn}

>>>>

We present the interface of quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe}. We use this particular QFHE because it allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{Enc}$ can be done classically.
	\item $\mathsf{Dec}$ commutes with standard basis measurement. If the ciphertext is a measurement result, it can also be done classically.
\end{itemize}
